Articles of Association of London Hackspace Ltd.

### 2011-07-16 constitution/articles-body.tex
Some more OCO stuff I missed. General tidying up.

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment for the use of the residents of London.
  \end{enumerate}

@@

      paragraph (i) or (ii)above;

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the charity unless, after
    the resignation, there would be less than two members;
  \item
    any sum due from the member to the charity is not paid in full
    within six months of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the charity that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the charity) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

\section{General Meetings}

\item
  \begin{enumerate}
  \item
    The charity must hold its first annual general meeting within
    eighteen months after the date of its incorporation.
  \item
    An annual general meeting must be held in each subsequent year and
    not more than fifteen months may elapse between successive annual
    general meetings.
  \end{enumerate}
\item
  The directors may call a general meeting at any time.

@@

@@

\section{Minutes}

\item
  The directors must keep minutes of all:
  \begin{enumerate}
  \item
    appointments of officers made by the directors;
  \item
    proceedings at meetings of the charity;
  \item
    meetings of the directors and committees of directors including:
    \begin{enumerate}
    \item
      the names of the directors present at the meeting;
    \item
      the decisions made at the meetings; and
    \item
      where appropriate the reasons for the decisions.
    \end{enumerate}
  \end{enumerate}

@@

\section{Annual Report and Return and Register of Charities}

@@

\item
  \begin{enumerate}
  \item
    Proof that an envelope containing a notice was properly addressed,
    prepaid and posted shall be conclusive evidence that the notice was
    given.
  \item
    Proof that an electronic form of notice was given shall be
    conclusive where the company can demonstrate that it was properly
    addressed and sent, in accordance with section 1147 of the
    Companies Act 2006.
  \item
    In accordance with section 1147 of the Companies Act 2006, notice
    shall be deemed to be given:
    \begin{enumerate}
    \item
      48 hours after the envelope containing it was posted; or
    \item
      in the case of an electronic form of communication, 48 hours after
      it was sent.
    \end{enumerate}
  \end{enumerate}

>>>>

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment in London.
  \end{enumerate}

@@

      paragraph (i) or (ii) above;

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the charity unless, after
    the resignation, there would be less than two members;
  \item
    any sum due from the member to the charity is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the charity that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the charity) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

\section{General Meetings}
\item
    The Board may convene a General Meeting whenever they think fit.

\item 
    General Meetings shall also be convened on such requisition, or in default may be convened by such
    requisitionists, as provided by section 304 of the Companies Act 2006.

@@

\item
    \begin{enumerate}
    \item
        The directors may delegate any of their powers or functions concerning the day
        to day management of the affairs of the Company to any person or persons as they may
        from time to time select.
    \item
        All acts done by a director shall, even if it is afterwards discovered that there was
        a defect in their appointment or that they were disqualified from holding office or had
        vacated office, be as valid as if such person had been duly appointed and was qualified
        and had continued to be a director.
    \item
        Where on any particular occasion more than 2 directors, in the course of their
        office as directors, discuss the affairs of the Company by any means, whether in person
        or otherwise, a minute shall be made and recorded indicating:
            \begin{enumerate}
                \item
                    when the discussion took place;
                \item
                    the identities of the directors involved; and
                \item
                    the identities of the directors involved; and
            \end{enumerate}
    \item
        Minutes of directors meetings:
            \begin{enumerate}
                \item
                    may be held in electronic form, and in particular using the Governance System;
                \item
                    must be held for ten years from the date of the discussion in accordance with section
                    248 of the Companies Act 2006.
            \end{enumerate}
    \end{enumerate}

@@

@@

\section{Annual Report and Register of Charities}

@@

\item
  \begin{enumerate}
  \item
    Proof that an envelope containing a notice was properly addressed,
    prepaid and posted shall be conclusive evidence that the notice was
    given.
  \item
    Proof that an electronic form of notice was given shall be
    conclusive where the company can demonstrate that it was
    accepted by an electronic mail host for that address
  \item
    In accordance with section 1147 of the Companies Act 2006, notice
    shall be deemed to be given:
    \begin{enumerate}
    \item
      48 hours after the envelope containing it was posted; or
    \item
      in the case of an electronic form of communication, 48 hours after
      it was sent.
    \end{enumerate}
  \end{enumerate}
